Selecting and ranking interesting pairs of cyclic temporal granularities

### 2021-01-12 paper/main.Rmd
improvise simulations writeup

Figure \ref{fig:normal-diff-quantrans} and \ref{fig:gamma-diff-quantrans} show distribution of wpd for different initial normal and gamma distribution to study the effect of changing location and scale on the distribution of wpd. It seems like the  distribution changes across different facet and x levels but look the same for each panel, which implies wpd value is unaffected by the change in location and scale of the the normal distribution. Figure \ref{fig:mean-sd-ns-nfacet} shows how mean and sd of the distribution of wpd changes with the increasing x and facet levels. It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels. Figure \ref{fig:nxbyfacet-ridge-N05} gives another way to look at the effect of changing facet and x levels on the distribution of wpd for an initial distribution $N(0,5)$. Clearly, the location of the distribution shifts to the right for increasing x levels and scale is different for low and high values of facet levels with a longer left tail for lower facet levels. We have considered alternate distribution, location and scale for this simulation setting, but do not present the results as they are behaviorally similar.

<!-- # ```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution. The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution", eval = FALSE} -->
<!-- # knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png")) -->
<!-- # ``` -->

```{r normal-diff-quantrans, fig.cap = "Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution. The densities change across different facet and x levels but look same for each panel, which implies wpd value is unaffected by the change in mean and standard deviation of the normal distribution"}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
```

```{r gamma-diff-quantrans, fig.cap="Ridge plots of raw wpd is shown for Gamma(0.5,1), Gamma(2,1) distribution. The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change in the shape paramter of the gamma distribution"}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
```

@@

```{r nxbyfacet-ridge-N05, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution. For each panel, it could be seen that the location shifts to the right for increasing x levels. Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N05.png"))
```

>>>>

Figure \ref{fig:normal-diff-quantrans} shows distribution of wpd for initial distribution N(0,1), N(5,1) and N(0,5) to study the effect of changing location and scale on the distribution of wpd. It seems like the  distribution changes across different facet and x levels but look the same for each panel, which implies wpd value is unaffected by the change in location and scale of the the normal distribution.

Figure \ref{fig:mean-sd-ns-nfacet} shows how mean and sd of the distribution of wpd changes with the increasing x and facet levels. It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.

```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution. The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution", eval = FALSE}
knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png"))
```

```{r normal-diff-quantrans, fig.cap="Ridge plots of raw wpd is shown for N(0,1), N(5,1) and N(0,5) distribution. The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution"}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_normal.png"))
```

@@
